SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-05-14 scipy-1.0/paper.tex
Swap subsections in Project Organization (#128)
* Swap subsections in Project Organization
The "Governance" and "Maintainers and contributors" subsections are focused on SciPy itself (internal). "Commmunity beyond the SciPy library" is about relationships with other projects (external), but its sandwiched between the other two internal sections. I changed the order of subsections to "Governance", "Maintainers and contributors", and "Community beyond the SciPy library"; they are now in order from closest to the core of the project to further away.

* Attempt to incorporate @ilayn's comments

"I

@@

The SciPy project has approximately 15 active maintainers---people who review
others' contributions, and in general do everything needed to ensure that the
software and the project move forward. Maintainers are critical to the health
of the project\cite{eghbal2016}; their skills and efforts largely determine how
fast the project moves forward, and they enable contributions from a much
larger group. Accordingly, the project also has an additional ~100 unique
contributors for every 6-monthly release cycle. Anyone with the interest and
skills can become a contributor or maintainer; the SciPy Developer
Guide\cite{scipy-dev-guide} provides guidance on how to do that.

>>>>

The SciPy project has approximately 100 unique contributors
for every 6-monthly release cycle. Anyone with the interest and
skills can become a contributor; the SciPy Developer
Guide\cite{scipy-dev-guide} provides guidance on how to do that.
In addition, the project currently has 15 active maintainers: people who review
the contributions of others and do everything else needed to ensure that the
software and the project move forward. Maintainers are critical to the health
of the project\cite{eghbal2016}; their skills and efforts largely determine how
fast the project moves forward, and they enable input from the much
larger group of contributors. Anyone can become a maintainer, too, as they
are selected on a rolling basis from contributors with a significant history of
high-quality contributions.

@@
